\chapter{Interview Guide}
\label{interview_guide}

\subsubsection{Introduction and Information}

\begin{itemize}
	\item Background on research study and what the information will be used for
	\item Inform about interview being recorded
	\item Inform about anonymity
	\item Inform about the participation being voluntary
	\item Describe what will happen at the end of the study
\end{itemize}

\subsubsection{Organisation}

\begin{itemize}
	\item Draw teams and communication arenas between teams
	\item Who were sitting where?
\end{itemize}

\subsubsection{Timeline Exercise}

\begin{itemize}
	\item Identify important events in the project
\end{itemize}

\subsubsection{Inter-team Coordination}

\begin{itemize}
	\item How was the work organised in your part of the project?
	\item What kind of dependencies were there between the teams in your part of the project? Examples?
	\item How were dependencies managed? Examples?
	\item What was managed in established forums and what was managed outside of the forums? Examples?
	\item Who were involved in managing dependencies between teams? Examples?
	\item Did you encounter challenges with managing dependencies? Examples?
	\item Did you change the way you managed dependencies during the project? Examples?
	\item What practices do you think were most important in order to manage dependencies between teams? Examples?
	\item Are there any practices you think had little importance for managing dependencies?
	\item How did the division of the project into three main parts influence the coordination between teams?
	\item Were there differences in inter-team coordination across the sub-projects?
\end{itemize}

\subsubsection{Knowledge Sharing}

\begin{itemize}
	\item What type of knowledge was important to share between teams in this project?
	\item What kind of practices were used in order to share knowledge?
	\item How would you evaluate the different practices used?
	\item Was there any knowledge that was difficult to share?
	\item Is it possible to identify ``knowledge communities'' within the project?
	\item Which of these communities were official and which were unofficial?
	\item How was the work organised within the communities?
	\item How was knowledge sharing influenced by having several companies working together in the project?
	\item Which knowledge sharing arenas would you argue were most important for the project?
	\item Did a team know what other teams were working on?
	\item Were you able to shift workload across teams? Why was this easy/hard?
	\item Were there any tool support?
\end{itemize}

\subsubsection{Retrospective}

\begin{itemize}
	\item What worked well?
	\item What was challenging?
\end{itemize}