\chapter*{Preface}

I am now entering my last year on a master degree in computer science where I specialise in software, or more specifically, software systems. I was introduced to agile development methodologies through different subjects at the ``Norwegian University of Science and Technology'', NTNU, and also got hands-on experience working with Scrum in a subject called ``TDT4290 - Customer Driven Project''. This subject in particular sparked my interest in agile development methodologies and the new ways of handling work and project organisation. After a summer internship with EY (formerly known as Ernst\&Young) I got more intrigued with how communication and coordination was handled in real life business and IT projects. Therefore, my previous experiences led to a motivation in exploring the combination of agile development and coordination.

The work performed in this pre-study is carried out to give an insight in the field of coordination in large-scale agile software development projects. This insight will be of considerable importance for a planned master thesis prepared for my last semester at NTNU.

I would like to use this opportunity to thank Torgeir Dingsøyr for his support, assistance and knowledge throughout the research project as the advisor. I would also like to thank NTNU for giving me the opportunity to experiment with ideas within the boundaries of the research project, and letting me acquire interesting knowledge for the future.

\vspace{1.5cm}

Trondheim, \today

\newcommand{\singleSignature}[1]{
\vspace{0.5cm}


\noindent
%\begin{}


    \vspace{0.5cm}

    \begin{tabular}{l}
    \rule{6cm}{1pt}\\
    #1
    \end{tabular}
%\end{}

\vspace{1cm}
}

\singleSignature{Espen Andreassen}